Conditions for $d$-local-connectedness of boundaries of hyperbolic groups

### 2020-02-18 paper.tex
Made clearer the application of the special homotopy proposition

  \todo{This still doesn't feel quite there yet.}
  For each $m$ we can apply Proposition~\ref{prop:basic_homotopies} to the maps
  $f_{m+1}$ and $i^{n+m}_{n+m+1}\composed f_m$: Lemma~\ref{lem:name_this} gives
  the bounded distance assumption, $f_{m+1}$ is a simplicial approximation to
  $p^\infty_{n+m+1}\composed\gamma$, and $i^{n+m}_{n+m+1}\composed f_{m+1}$ is
  also a simplicial approximation to a map that factors through
  $p^\infty_{n+m+1}$ because the restriction of $i^{n+m}_{n+m+1}$ to $\Skel_1
  K_{n+m}$ has this property.

>>>>

  For each $m$ we can apply Proposition~\ref{prop:basic_homotopies} to the maps
  $f_{m+1}$ and $i^{n+m}_{n+m+1}\composed f_m$. To see this, firstly
  Lemma~\ref{lem:name_this} gives the uniformly bounded distance assumption.
  Secondly, $f_{m+1}$ is a simplicial approximation to
  $p^\infty_{n+m+1}\composed\gamma$. Finally,
  $i^{n+m}_{n+m+1}\restricted{\Skel_1 K_{n+m}}$ is a simplicial approximation
  to a map $p^\infty_{n+m+1}\composed j_m$ for some map $j_m\from\Skel_1
  K_{n+m}\to \boundary G$, and then $i^{n+m}_{n+m+1}\composed g_m$ is a
  simplicial approximation to $p^\infty_{n+m+1}\composed j_m\composed f_m$.
